---
title: "RMarkDown_Lego#3"
output: html_document
date: "2023-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
summary(cars)
```
##USING VECTORS

##1. There is a built-in vector LETTERS contains the uppercase letters of the alphabet and letters which contains the lowercase letters of the alphabet.

```{r}
LETTERS

letters
```
#a.You need to produce a vector that contains the first 11 letters.
```{r}
num1<- LETTERS[c(1:11)]
num1
```
#b. Produce a vector that contains the odd numbered letters.
```{r}
LETTERS
odd<-LETTERS[seq( 2, 26, by=2 )]
odd
```
##c. Produce a vector that contains the vowels
```{r}
LETTERS
vowels<-LETTERS[c( 1, 5, 9, 15, 21)]
vowels
```
#Based on the above vector letters:
#d. Produce a vector that contains the last 5 lowercase letters.
```{r}
num1_d<- letters[c(22,23,24,25,26)]
num1_d
```
#e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r}
num1_e<- letters[seq(15, 24, by=1)]
num1_e
```

##2. Create a vector(not a dataframe) with the average temperatures in April for Tugue-garao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
#a. What is the R code and its result for creating a character vector for the city/town of Tuguegarao City, Manila, Iloilo City, Tacloban,Samal Island, and Davao City? Name the object as city. The names should follow the same order as in the instruction.
```{r}
city<- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
city
```
#b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
#Name the object as temp. Write the R code and its output. Numbers should also follow what is in the instruction.
```{r}
temp<- c( 42, 39, 34, 34, 30, 27)
temp
```
#c. Create a dataframe to combine the city and the temp by using ‘data.frame(). What is the R code and its result?
```{r}
num2_c<-data.frame(
  city = c(city),
  temp = c( temp)
)
num2_c
```
  
#d. Associate the dataframe you have created in 2.(c) by naming the columns usingthe names() function. Change the column names by using names() function as City and Temperature. What is the R code and its result?
```{r}
colnames(num2_c)<-c("City", "Temperature")
num2_c
```
##e. Print the structure by using str() function. Describe the output.
```{r}
str(num2_c)
```

##f. From the answer in d, what is the content of row 3 and row 4 What is its R code and its output?
```{r}
num2_c[3:4,]
```

##g. From the answer in d, display the city with highest temperature and the city with the lowest temperature.
#What is its R code and its output?
```{r}
max(city)
min(temp)
```
#USING MATRICES
